Non-negligible Effects of Electronic Polarization at Negatively Charged Membranes with Ions

### 2019-05-08 Manuscript/manuscript.tex
Small edits

%%SAMULI: new suggestion for the preliminary title
\title[] 
  { Non-negligible Effects of Electronic Polarization at Negatively Charged Membranes and ions }

@@

More recently, classical molecular dynamics (MD) simulations
have been used to support the interpretation of spectroscopic experiments,
but the results strongly depend on the force field parameters \cite{boettcher11,kucerka14,melcrova16,hallock18,valentine18}.
For instance, the moieties of PS lipids that interact with calcium cations vary greatly.
In simulations with the CHARMM36 force field \cite{klauda10,venable13} using the NBfix parameters for calcium \cite{kim16}, 
calcium ions interact only with the carboxylate group of PS lipids \cite{valentine18}.
However, the same force field without the NBfix parameters, gives a significant binding affinity also to the phosphate region \cite{hallock18}.
On the other hand, simulations with the Berger force field \cite{berger97,mukhopadhyay04}
suggest a significant calcium binding also to the carbonyls in the acyl chains \cite{melcrova16}.

@@

%In contrast, the combination of NMR experiments 
%and MD simulations with the same model, CHARMM36, but without the correction for calcium binding
%also reveal long-lived interactions of \ce{Ca^{2+}} with \ce{PO4} groups. \cite{hallock18}
%Although the ratios of the life times of coordination follow the same trends as in our work,
%the lengths of simulation trajectories are insufficient 
%to yield converged results in this aspect (see SI and Refs.~\cite{catte16, melcr18, NMRlipidsIV}). 
\begin{table}[tb!] 
\centering
\caption{%Bulk concentrations, $C _{Ca}$, and buffer concentrations, $C' _{Ca}$, of Ca$^{2+}$;
  % relative surface excess of calcium with respect to water ($\Gamma_{Ca}^{\rm water}$); 
  % and
  Percentages of the population of bound Ca$^{2+}$ to various lipid moieties in a pure POPC bilayer with 350 mM CaCl$_2$
  and in a POPC:POPS (5:1) mixture with 409 mM CaCl$_2$. The threshold for counting a contact was set to $0.3\,\mathrm{nm}$, which encompasses the
  first peak of the radial distribution function between the cations and the oxygen atoms of the lipids. 
  \label{tab:binding}} 
\begin{tabular}{ l | c c } 
        interacting moiety    &  \multicolumn{2}{c}{percentage of bound \ce{Ca^{2+}} } \\
%	\hline
%	$C _{Ca}\,/\,\mathrm{mM}$  &  $240\pm 10 $  &  $280\pm 10 $  \\
%	$C'_{Ca}\,/\,\mathrm{mM}$  &  $400\pm 10 $  &  $350\pm 10 $  \\
%	$\Gamma_{Ca}^{\rm water}\, / \,\mathrm{nm}^{-2}$  &  $0.24 \pm 0.01 $  &  $0.06 \pm 0.01 $  \\
%	\hline
%                             &  \multicolumn{2}{c}{ } \\
                             &  5\,POPC:1\,POPS &  POPC   \\
	\hline
	     PC              &   59   &  100   \\
	     PO$_4$    in PC &   41   &   67   \\
	     carbonyls in PC &   <1   &   ~1   \\
	\hline
	     PS              &    8   &        \\ 
	     PO$_4$  in PS   &    2   &        \\
	     COO$^-$ in PS   &    4   &        \\
	     carbonyls in PS &   <1   &        \\
	\hline
	both PC and PS       &   33   &        \\
  \end{tabular} \\
  \todo{I have commented out the surface excess values (available in text) and concentrations (now in caption) from the table.} \\
  \todo{I do not understand the numbers for different moieties. Are these probabilities that the calcium binds only to these moieties and
    nothing else? In total, 41 \% binds to PS lipids, but only 2 \% and 4 \% to phosphates and COO$^-$, respectively? Where do the rest bind?
    I think that we should show the total probabilities to bind to different moieties.}
\end{table}

>>>>

%%SAMULI: new suggestion for the preliminary title
\title[] 
  { Non-negligible Effects of Electronic Polarization at Negatively Charged Membranes with Ions }

@@

More recently, classical molecular dynamics (MD) simulations
have been used to support the interpretation of spectroscopic experiments,
but the results strongly depend on the force field parameters \cite{boettcher11,kucerka14,melcrova16,hallock18,valentine18}.
% smoother connection between previous and following statements
For instance, the moieties of PS lipids that interact with calcium cations vary greatly.
In simulations with the CHARMM36 force field \cite{klauda10,venable13} using the NBfix parameters for calcium \cite{kim16}, 
calcium ions interact only with the carboxylate group of PS lipids \cite{valentine18}.
However, the same force field without the NBfix parameters, gives a significant binding affinity also to the phosphate region \cite{hallock18}.
On the other hand, simulations with the Berger force field \cite{berger97,mukhopadhyay04}
suggest a significant calcium binding also to the carbonyls in the acyl chains \cite{melcrova16}.

@@

%In contrast, the combination of NMR experiments 
%and MD simulations with the same model, CHARMM36, but without the correction for calcium binding
%also reveal long-lived interactions of \ce{Ca^{2+}} with \ce{PO4} groups. \cite{hallock18}
%Although the ratios of the life times of coordination follow the same trends as in our work,
%the lengths of simulation trajectories are insufficient 
%to yield converged results in this aspect (see SI and Refs.~\cite{catte16, melcr18, NMRlipidsIV}). 
\begin{table}[tb!] 
\centering
\caption{%Bulk concentrations, $C _{Ca}$, and buffer concentrations, $C' _{Ca}$, of Ca$^{2+}$;
  % relative surface excess of calcium with respect to water ($\Gamma_{Ca}^{\rm water}$); 
  % and
  Percentages of the population of bound Ca$^{2+}$ to various lipid moieties in a pure POPC bilayer with 350 mM CaCl$_2$
  and in a POPC:POPS (5:1) mixture with 409 mM CaCl$_2$. The threshold for counting a contact was set to $0.3\,\mathrm{nm}$, which encompasses the
  first peak of the radial distribution function between the cations and the oxygen atoms of the lipids. 
  \label{tab:binding}} 
\begin{tabular}{ l | c c } 
 exclusive interacting moiety &  \multicolumn{2}{c}{percentage of bound \ce{Ca^{2+}} } \\
%	\hline
%	$C _{Ca}\,/\,\mathrm{mM}$  &  $240\pm 10 $  &  $280\pm 10 $  \\
%	$C'_{Ca}\,/\,\mathrm{mM}$  &  $400\pm 10 $  &  $350\pm 10 $  \\
%	$\Gamma_{Ca}^{\rm water}\, / \,\mathrm{nm}^{-2}$  &  $0.24 \pm 0.01 $  &  $0.06 \pm 0.01 $  \\
%	\hline
%                             &  \multicolumn{2}{c}{ } \\
                             &  5\,POPC:1\,POPS &  POPC   \\
    \hline
    \textbf{PC}              &   59   &  100   \\
	     PO$_4$    in PC &   41   &   67   \\
	     carbonyls in PC &   <1   &   ~1   \\
    \hline
    \textbf{PS}              &    8   &        \\ 
	     PO$_4$  in PS   &    2   &        \\
	     COO$^-$ in PS   &    4   &        \\
	     carbonyls in PS &   <1   &        \\
    \hline
    \textbf{both PC and PS}  &   33   &        \\
  \end{tabular} \\
  %\todo{I have commented out the surface excess values (available in text) and concentrations (now in caption) from the table.} \\
  %\todo{I do not understand the numbers for different moieties. Are these probabilities that the calcium binds only to these moieties and
  %  nothing else? In total, 41 \% binds to PS lipids, but only 2 \% and 4 \% to phosphates and COO$^-$, respectively? Where do the rest bind?
  %  I think that we should show the total probabilities to bind to different moieties.}
\end{table}
